Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-26 paper_jasa.tex
loess picture updated
figure for choice reason updated
experiment 3 reasoning plot updated

In all the three experiments, each subject saw a lineup only once. This allows no random effect for lineup and this simplifies model \ref{mixed} as $\tau_{\ell  i}=\tau_i$.   This gives us the estimate of subject specific probability of successful evaluation of a lineup ($\hat p_i$) from model \ref{mixed}. Parameter estimates of the model is shown in table \ref{tbl:model_par}.  The estimated subject specific power curves are shown in figure \ref{fig:power_mixed_subject}. Subject specific power is quite different for three experiments. It appears that scatter plot serves better job compared to box plot as a visual test statistic. But subject to subject variability is larger in scatterplot as we see in figure \ref{fig:power_mixed_subject} for experiment 2 and 3.

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
       \caption{Reasons for choosing the plot in a lineup for experiment 3. Reasons 1 = Most different plot,  2 = Visible trend,  3 = Clustering visible,  4= Other.  Reason 12 means both reasons 1 and 2 are chosen. Notice that 345 people choose only reason 3 out of whom 64\% got the actual plot (proportion correct = 0.64), which indicates there are number of people who choose the right plot for wrong reason (Type-III error). Those who chose reason 123 got the actual plot about 100\% times.}
       \label{fig:choice_reason}
\end{figure}

>>>>

In all the three experiments, each subject saw a lineup only once. This allows no random effect for lineup and this simplifies model \ref{mixed} as $\tau_{\ell  i}=\tau_i$.   This gives us the estimate of subject specific probability of successful evaluation of a lineup ($\hat p_i$) from model \ref{mixed}. Different subject performs differently depending on effect as well. So, we include a random interaction term with effect. Parameter estimates of the model is shown in table \ref{tbl:model_par}.  The estimated subject specific power curves are shown in figure \ref{fig:power_mixed_subject}. Subject specific power is quite different for three experiments. It appears that scatter plot serves better job compared to box plot as a visual test statistic. But subject to subject variability is larger in scatterplot as we see in figure \ref{fig:power_mixed_subject} for experiment 2 and 3.

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
       \caption{Reasons for choosing the plot in a lineup for experiment 3. Reason 12 means both reasons 1 and 2 are chosen. Number of subjects choosing that reason are shown on the right hand side. Notice that 345 people choose only reason (3) "Clustering visible", out of whom 64\% got the actual plot (proportion correct = 0.64), which indicates there are number of people who choose the right plot for wrong reason (Type-III error). Those who chose reason 123 got the actual plot about 97\% times.}
       \label{fig:choice_reason}
\end{figure}
